Croder: Bringing the Knowledge of the Crowds into the IDE

### 2013-05-03 paper/paper.tex
Added a reference to Brian's paper
Added the abstract

@@

Interruptions are bad because they break the flow of work and cause more stress \cite{Spolsky,Mark2008}. 
Also, the interruptions that a developers faces are varied \cite{Czerwinski2004}, so trying to reduce that number
will bring benefit to the workflow. By integrating the code review submission process into the \ide we can 
reduce the time of the interruption. Also, because the developer never leaves the context of his work, we hope 
that the effects of this interruption will be minimal.

>>>>

\begin{abstract}
This paper presents a new way of doing code reviews. Since they take up a lot of time and require
a great amount to coordination. We propose a new way doing reviews using the crowds. By 
integrating the \ide{}'s with the review platform we hope to make it easier for developers to review
code and have code reviews. To test our proposed solution, we have built a new tool, \croder{}, that
can pot reviews and get results from StackExchange. This integration will help developers post
tasks without the need of context switching.
\end{abstract}

@@

Interruptions are bad because they break the flow of work and cause more stress \cite{Spolsky,Mark2008}. 
Also, the interruptions that a developers faces are varied \cite{Czerwinski2004}, so a solution that reduces
the number of interruptions is essential. \cite{Adamczyk2004}. By integrating the code review submission 
process into the \ide we can  reduce the time of the interruption. Also, because the developer never leaves 
the context of his work, we hope that the effects of this interruption will be minimal.
